---
title: "Create Condensed Datafiles"
author: "Christina Bonsell"
date: "October 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(readxl)
```

#Created condensed insitu logger datafiles for easier submission to repository



#StarOddi load and munging

Combine
Insert Station name
Formate datetime

```{r}
filelist =list.files(path = ".", recursive = TRUE,
                     pattern = "\\.txt$", 
                     full.names = TRUE)
StarOddi <- filelist %>%
  set_names(.) %>%
  map_df(read_table2, col_names = FALSE, .id = "FileName",
         col_types = cols(X4 = col_character(),
                          X5 = col_character(), 
                          X6 = col_character(), 
                          X7 = col_character()))

#change from european to SI notation
StarOddi$X4<-as.numeric(sub(",", ".", StarOddi$X4, fixed = TRUE))
StarOddi$X5<-as.numeric(sub(",", ".", StarOddi$X5, fixed = TRUE))
StarOddi$X6<-as.numeric(sub(",", ".", StarOddi$X6, fixed = TRUE))
StarOddi$X7<-as.numeric(sub(",", ".", StarOddi$X7, fixed = TRUE))

StarOddi<-StarOddi%>%mutate(Station=str_sub(FileName,15,19))%>%
                              select(Station, Date=X2, Time=X3, Temp_C=X4, Sal=X5, Cond_mspercm=X6, SoundVel_mpers=X7)

StarOddi$DT<-as_datetime(paste(as.Date(StarOddi$Date, format="%d.%m.%Y"), StarOddi$Time))
```


#RBR load and munging

Combine
Insert Station name
Format Datetime
Get rid of unneeded columns

```{r}
filelist =list.files(path = ".", recursive = TRUE,
                     pattern = "\\.xls$", 
                     full.names = TRUE)
RBR <- filelist %>%
  set_names(.) %>%
  map_df(read_excel, col_names = T, .id = "FileName")
#Don't know what cols 11(temp?) and 12 are

RBR<-RBR%>%mutate(Station=str_sub(FileName,29,33), DT=as.POSIXct(Timestamp, format="%d/%m/%Y %H:%M:%OS"))%>%
  select(-Timestamp, -FileName, -...11, -...12)
RBR<-RBR[,c(10,11,1:9)]# reorder columns

```



#TCM Temp load and munging

Combine
Insert Station name
Format datetime

```{r}
filelist =list.files(path = ".", recursive = TRUE,
                     pattern = "\\Temperature.csv$", 
                     full.names = TRUE)
TCM_Temp <- filelist %>%
  set_names(.) %>%
  map_df(read_csv, .id = "FileName")

TCM_Temp<-TCM_Temp%>%mutate(Station=str_sub(FileName,21,25))%>%
  select(Station, DT=`ISO 8601 Time`, Temperature=`Temperature (C)`) 
```


#TCM Current loading and munging

Settings from Lowell software data conversion:

TCMs: 0 ballast, Salt water

Declination (WMM, 1 April 2019) set for TCMS:

 * EEL and EWL: 13.86
 
 * KAL and JAL:19.07
 
 
```{r}
filelist =list.files(path = ".", recursive = TRUE,
                     pattern = "\\Current.csv$", 
                     full.names = TRUE)
TCM_Curr <- filelist %>%
  set_names(.) %>%
  map_df(read_csv, .id = "FileName")

TCM_Curr<-TCM_Curr%>%mutate(Station=str_sub(FileName,21,25))%>%
  select(Station, DT=`ISO 8601 Time`, Speed_cm_s=`Speed (cm/s)`, Heading= `Heading (degrees)`,
         Vel_N=`Velocity-N (cm/s)`, Vel_E=`Velocity-E (cm/s)`)
```

#Write files
```{r}
write.csv(RBR, "RBR_condensed_raw.csv")
write.csv(StarOddi, "StarOddi_condensed_raw.csv")
write.csv(TCM_Temp, "TCMtemperature_condensed_raw.csv")
write.csv(TCM_Curr, "TCMcurrent_condensed_raw.csv")
```

