---
title: "CTD QAQC for repository"
author: "Christina Bonsell"
date: "October 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Important info

* Data come from either RBR CTDs of Star Oddi CSTs (this code puts both into final dataset)
* EWLD1 and KALD1 (Star Oddi) were calibrated based on YSI sonde measurements, other stations looked good
    + KALD1 calibrated for Temp and Cond, EWLD1 calibrated for Cond
* EELD1 got buried, was recording sediment temperature. Data flagged as **QM** (questionable) by trained human. Temperature data looks ok (but with low max temps), use with caution. 
* Data below freezing line flagged as **INV** (invalid) by algorithm
* Other suspicious data (big linear drops in cond/sal) flagged as **QM** by trained human. These drops are common in areas with high turbidity and are caused by obstructions (such as sediment) the conductivity cup.


## Work-up code and plots:

Required packages:

```{r libs, echo=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(cowplot)
library(devtools)
#devtools::install_github("atn38/insitu", force=TRUE)
library(insitu)
```


Read in data
```{r ysi_data, message=FALSE, warning=FALSE}

RBR <- read_csv("RBR_condensed_raw.csv") %>% janitor::clean_names()# change colnames to lowercase


StarOddi <- read_csv("StarOddi_condensed_raw.csv", col_types = cols(date_time = col_datetime(format = "%m/%d/%Y %H:%M"))) 

YSI <- read_csv("YSI_for_calibration.csv", col_types = cols(date_time = col_datetime(format = "%m/%d/%Y %H:%M")))
```


(re)Calibrate if needed

* EWLD1 and KALD1 (Star Oddi) were calibrated based on YSI sonde measurements, other stations looked good
    + KALD1 calibrated for Temp and Cond, EWLD1 calibrated for Cond


create calibrated data, in dataframe, and a column for which parameter is calibrated
```{r cal_EWLD_KALD1_new, message=FALSE, warning=FALSE}
to_cal<-StarOddi%>%filter(station=="EWLD1"|station=="KALD1")
calibrated_cond <- calibrate_data(to_cal, YSI, cal_by = "conductivity", raw="conductivity")%>% 
  select(-conductivity) %>% 
  rename(conductivity=conductivity_calibrated)

KALD1<-StarOddi%>%filter(station=="KALD1")
KALD1c <- calibrate_data(KALD1, YSI, cal_by = c("temperature"), raw=c("temperature")) %>% 
  select(-temperature) %>% 
  rename(temperature= temperature_calibrated)

calibrated <- left_join(calibrated_cond,KALD1c) %>% 
  select(station,date_time, temperature, conductivity, sound_vel) %>% 
  mutate(recalibrated_parameters=case_when(station=="EWLD1"~"T",
                                         station=="KALD1"~"CT"))

calibrated_cond <- calibrate_data(to_cal, YSI, cal_by = "conductivity", raw="conductivity")
```

re-Merge and format StarOddi data
derive salinity using UNESCO 1983 (=PSS-78)

```{r SO_format, message=FALSE, warning=FALSE}
StarOddi <- StarOddi%>%filter(station !="KALD1"& station!="EWLD1")%>%
  bind_rows(calibrated) %>% 
  select(station, date_time, temperature, conductivity, salinity, speed_of_sound=sound_vel, recalibrated_parameters)


StarOddi$salinity <- round(calculate_salinity(StarOddi$conductivity, StarOddi$temperature), digits=2)

```

Identify/flag invalid data from freezing line

```{r freeze_flag, message=FALSE, warning=FALSE, fig.width=11}

StarOddi %>% filter(station=="EWLD2") %>% 
  plot_tempsal(.,"temperature","salinity","date_time", plottitle="Example of dataset with invalid data")

StarOddi <- flag_salinity(StarOddi, Terror=.1, Cerror = 2, flag_scheme = c("VALID","INV"))

RBR <- flag_salinity(RBR, Terror=.002, Cerror = .01, flag_scheme = c("VALID","INV"))


ggplot(StarOddi, aes(date_time, salinity))+
  geom_point(aes(color=anomalous))+
  facet_wrap(~station)+
  theme_cowplot()


ggplot(RBR, aes(date_time, salinity))+
  geom_point(aes(color=anomalous))+
  facet_wrap(~station)+
  theme_cowplot()
```

Manually flag questionable data, choose which dataset to put in final dataframe if there are both RBR and Star Oddi at a station

```{r manual_flag,  echo=FALSE, warning=FALSE, message=FALSE}

x<-RBR%>%group_split(station)

#####################
###use this function to determine index of questionable data
# id_outlier(as.data.frame(x[2]), plot_type = "sal/time")
# id_outlier(as.data.frame(x[2]), plot_type = "temp/sal")
#####################

EWLD2<-as.data.frame(x[2])
EWLD2$anomalous[c(2901,4935:5108,5793:5962,7179,8217:8244)]<-"QM"
JALD2<-as.data.frame(x[3])
KALD2<-as.data.frame(x[4])

RBR_flagged<-bind_rows(EWLD2,JALD2,KALD2) 

x<-StarOddi%>%group_split(station)

EELD1<-as.data.frame(x[1])
EELD1$anomalous[c(482:nrow(EELD1))]<-"QM"

EELD2<-as.data.frame(x[2])
EELD2$anomalous[c(1:15,7127:7519)]<-"QM"

EWLD1<-as.data.frame(x[3])
EWLD1$anomalous[7524]<-"QM"

JALD1<-as.data.frame(x[5])
JALD1$anomalous[c(2984,3387,7676:7891)]<-"QM"

KALD1<-as.data.frame(x[7])
KALD1$anomalous[c(8:194,7641:8333)]<-"QM"


SO_flagged<-bind_rows(EELD1,EELD2,EWLD1,JALD1,KALD1)

```

Create final datatables for each instrument
designate cond/sal flags vs temperature flags

```{r flagged_table, echo=FALSE, warning=FALSE, message=FALSE}
RBR_final<-RBR_flagged%>%rename(flags_condsal=anomalous) %>% 
  mutate(instrument="RBR")

SO_final<-SO_flagged %>% 
  mutate(flags_temperature=case_when(anomalous=="QM" & station=="EELD1" ~ "QM", 
                                     TRUE ~ "VALID"),
         instrument="StarOddi")%>%
  rename(flags_condsal=anomalous)
```

# Finalize table into combined, derived "CTD" data
CTD data table is nicely arranged

```{r finalize, warning=FALSE, message=FALSE, fig.width=11, fig.height=8, fig.fullwidth=TRUE}
#Finalize and write csvs

#RBR puts NA at date at daylight savings time, grrr
RBR_final<-RBR_final[!is.na(RBR_final$station),]
RBR_final$date_time<-force_tz(RBR_final$date_time, tz="UTC")
RBR_final$date_time[is.na(RBR_final$date_time)]<-as.POSIXct("2019-03-10 02:00:00", tz="UTC")

CTD <- bind_rows(RBR_final, SO_final) %>% 
  arrange(station, date_time) %>% #change row order
  select(station:date_time, instrument, recalibrated_parameters, conductivity:temperature, salinity, pressure:depth, speed_of_sound:density_anomaly, flags_condsal, flags_temperature) #change column order

CTD$recalibrated_parameters[is.na(CTD$recalibrated_parameters)] <- "NONE"
CTD$flags_temperature[is.na(CTD$flags_temperature)] <- "VALID"

```

check  data
```{r check}

summary(CTD)

table(CTD$station, CTD$instrument)#number of observations

table(CTD$station, CTD$flags_condsal)
table(CTD$station, CTD$flags_temperature)

CTD %>% group_by(station) %>% summarize(minD = min(date_time), maxD = max(date_time))#start and end date_time


```

Display data

```{r final_plots, warning=FALSE, message=FALSE, fig.width=11}
#plots
ggplot(CTD, aes(date_time, temperature))+
  geom_point(aes(color=flags_temperature),alpha=0.5)+
  facet_wrap(~station)+
  theme_cowplot()

ggplot(CTD, aes(date_time, salinity))+
  geom_point(aes(color=flags_condsal), alpha=0.5)+
  facet_wrap(~station)+
  theme_cowplot()

ggplot(CTD, aes(date_time, conductivity))+
  geom_point(aes(color=flags_condsal), alpha=0.5)+
  facet_wrap(~station)+
  theme_cowplot()

ggplot(CTD, aes(date_time, sea_pressure))+
  geom_point(aes(color=station), alpha=0.5)+
  theme_cowplot()
```

Write csv
```{r derived-data}
write.csv(CTD, "derived_BLE_insituCTD_2018to2019.csv")

```

