---
title: "CTD-QAQC"
author: "Christina Bonsell"
date: "October 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, message=FALSE}
library(tidyverse)
library(lubridate)
library(cowplot)
```

# A cleaned-up version of [CTDworkup-from-raw.Rmd](https://cbonsell.github.io/ble-instrumentation/CTDworkup-from-raw) that only returns final dataset and plots.

[R script for this document](https://github.com/cbonsell/ble-instrumentation/blob/master/CTD-QAQC.Rmd)

[R script for workup document](https://github.com/cbonsell/ble-instrumentation/blob/master/CTDworkup.Rmd)

Important info

* EWLD1 and KALD1 (Star Oddi) were calibrated based on YSI sonde measurements, other stations looked good
    + KALD1 calibrated for Temp and Cond, EWLD1 calibrated for Cond
* EELD1 looks like it got buried. Data flagged as QM (questionable) by trained human
* Data below freezing line flagged as INV (invalid) by algorithm
* Other suspicious data (big linear drops in cond/sal) flagged as QM by trained human


Read in data
```{r ysi_data, message=FALSE, warning=FALSE}

RBR <- read_csv("RBR_condensed_raw.csv") %>% select(-X1)
StarOddi <- read_csv("StarOddi_condensed_raw.csv") %>% select(-X1)

YSI <- read_csv("YSI_for_calibration.csv")
```



Calibrate EWLD1 and KALD1 data
```{r cal_EWLD_KALD1, message=FALSE, warning=FALSE}
source('scr/TScalibration_functions.R') #functions to calibrate temperature, conductivity and salinity, using YSI calibration measurements
source('scr/CondtoSal_miliS.R') #function to convert conductivity and temp to salinity


EWLD10<-StarOddi%>%filter(Station=="EWLD1")%>%
  left_join(YSI, by=c("Station","DT"))%>%
  mutate(row=1:which(DT==max(DT)))%>%
  rename(fixedCond=Conductivity, fixedTemp=Temperature)
dates<-which(!is.na(EWLD10$fixedCond))#identify where YSI measurements took place, ignore the June ones bc we were off Station
EWLD10$fixedCond[1]<-EWLD10$Cond_mspercm[1]#YSI reading in Aug 2018 doesn't make sense
EWLD10<-EWLD10[c(min(dates):max(dates)),]
EWLD1<-TSmidcal_SO(EWLD10,dates[2])
EWLD1$Salinity<-Cond.to.Sal(EWLD1$fixedCond,EWLD1$fixedTemp)

EWLD1$Station<-"EWLD1_calibratedTC"

EWLD1c<-EWLD1%>%mutate(Salinity=Cond.to.Sal(EWLD1$fixedCond,EWLD1$Temp_C))%>%
  select(-fixedTemp)%>%rename(fixedTemp=Temp_C)
EWLD1c$Station<-"EWLD1_calibratedCond"

KALD10<-StarOddi%>%filter(Station=="KALD1")%>%
  left_join(YSI, by=c("Station","DT"))%>%
  mutate(row=1:which(DT==max(DT)))%>%
  rename(fixedCond=Conductivity, fixedTemp=Temperature)
dates<-which(!is.na(KALD10$fixedCond))#identify where YSI measurements took place, ignore the June ones bc we were off Station
KALD10$fixedCond[1]<-KALD10$Cond_mspercm[1]#no YSI reading in Aug 2018
KALD10$fixedTemp[1]<-KALD10$Temp_C[1]
KALD10<-KALD10[c(1:max(dates)),]
KALD1<-TSmidcal_SO(KALD10,dates[1])
KALD1$Salinity<-Cond.to.Sal(KALD1$fixedCond,KALD1$fixedTemp)

KALD1$Station<-"KALD1_calibratedTC"

KALD1c<-KALD1%>%mutate(Salinity=Cond.to.Sal(KALD1$fixedCond,KALD1$Temp_C))%>%
  select(-fixedTemp)%>%rename(fixedTemp=Temp_C)
KALD1c$Station<-"KALD1_calibratedCond"

calibrated<-bind_rows(EWLD1,EWLD1c, KALD1, KALD1c)%>%
  select(-Temp_C,-Sal,-Cond_mspercm)%>%
  rename(Sal=Salinity,Temp_C=fixedTemp,Cond_mspercm=fixedCond)

StarOddi<-bind_rows(StarOddi,calibrated)
```

Identify invalid data from freezing line
```{r Id_anom, message=FALSE, warning=FALSE}
source('scr/TSoutliers_functions.R') #functions to identify invalid data from freezing line

RBR2<-TSanom_workup(RBR, "Temperature", "Conductivity", .002,.01)
SO2<-TSanom_workup(StarOddi, "Temp_C", "Cond_mspercm", .1,2)
```

Incorporate calibrated datasets for KALD1 and EWLD1
```{r calibrate, message=FALSE, warning=FALSE}
SO3<-SO2%>%filter(Station !="KALD1"&Station!="KALD1_calibratedCond"&
                    Station!="EWLD1"&Station!="EWLD1_calibratedTC")%>%
  mutate(Station=str_sub(Station,1,5),
         calibrated=case_when(Station=="KALD1"|Station=="EWLD1" ~ TRUE))
```

Created column that denotes data flags
```{r flag_data,  echo=FALSE, warning=FALSE, message=FALSE}
source('scr/data_flag.R')# script developed in data workup to ID questionable data

RBR_final<-RBR_flagged%>%mutate(flags=case_when(flag==T~"QM", anom==T~"INV"))
SO_final<-SO_flagged%>%mutate(flags=case_when(flag==T~"QM", anom==T~"INV"))
```

# Finalize tables
```{r finalize, warning=FALSE, message=FALSE, fig.width=11, fig.height=8, fig.fullwidth=TRUE}
#Finalize and write csvs

#RBR puts NA at date at daylight savings time, grrr
RBR_final<-RBR_final[!is.na(RBR_final$Station),]
RBR_final$DT<-force_tz(RBR_final$DT, tz="UTC")
RBR_final$DT[is.na(RBR_final$DT)]<-as.POSIXct("2019-03-10 02:00:00", tz="UTC")

# remove unneeded cols
RBR_final<-RBR_final%>%select(-anom, -flag)

SO_final<-SO_final%>%select(Station, DT, Temperature=Temp_C, Salinity=Sal, Conductivity=Cond_mspercm,
                             Speed.of.sound=SoundVel_mpers, flags,calibrated)



```

Display data

```{r}
#plots
ggplot(RBR_final, aes(DT, Temperature))+
  geom_point(aes(color=flags), alpha=0.5)+
  geom_point(data=SO_final, aes(DT, Temperature, color=flags), alpha=0.5)+
  facet_wrap(~Station)+
  theme_cowplot()

ggplot(RBR_final, aes(DT,Salinity))+
  geom_point(aes(color=flags), alpha=0.5)+
  geom_point(data=SO_final, aes(DT,Salinity, color=flags), alpha=0.5)+
  facet_wrap(~Station)+
  theme_cowplot()

ggplot(RBR_final, aes(DT, Conductivity))+
  geom_point(aes(color=flags), alpha=0.5)+
  geom_point(data=SO_final, aes(DT,Conductivity, color=flags), alpha=0.5)+
  facet_wrap(~Station)+
  theme_cowplot()

ggplot(RBR_final, aes(DT, Sea.pressure))+
  geom_point(aes(color=Station), alpha=0.5)+
  theme_cowplot()
```

Write csvs
```{r derived-data}
write.csv(RBR_final, "results/BLE LTER RBRCTD 2018to2019.csv")
write.csv(SO_final, "results/BLE LTER StarOddiCST 2018to2019.csv")
```

Final tables: 

[RBR](https://github.com/cbonsell/ble-instrumentation/blob/master/results/BLE%20LTER%20RBRCTD%202018to2019.csv)

[StarOddi](https://github.com/cbonsell/ble-instrumentation/blob/master/results/BLE%20LTER%20StarOddiCST%202018to2019.csv)
