---
title: "LTER Instrument Workup 2019"
author: "Christina Bonsell"
date: "Oct 4, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, echo=FALSE, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
library(viridisLite)
library(DT)
library(cowplot)
library(knitr)
```

## Temperature and Salinity Workup

#Initial conclusions/questions:
###1) Gotta throw out most, if not all EELD1 salinity data. I think these instruments ended up in the mud. Keep the StarOddi temp data from this station.
###2) RBR seems more accurate than Star Oddi* (e.g fewer big dips in salinity/conductivity), but still has a scatter of questionable conductivity data. There's no "cup" to be fouled by sediment, so what is happening?
###3) Some of the "non-anomoulus" data I would still throw out. After talking to Tim, this data should be left in but "flagged" in a new column. 

```{r ysi_data, echo=FALSE, include=FALSE, message=FALSE}
source('scr/CTDdata_import.R')
YSI<- read_csv("data/YSI 2018to2019.csv")%>%
  filter(DepthCat=="depth",Parameter %in% c("Temp.C","Sal","Cond"),
         !Station %in% c("SILD1","SILD2","STLD1","STLD2"))%>%
  select(Station,Parameter,Value,Datetime)%>%
  mutate(DT=round_date(Datetime, unit="hour"))%>%
  spread(Parameter, Value)%>%
  mutate(Conductivity=Cond/1000)%>%
  select(Station,DT,Salinity=Sal,Temperature=Temp.C, Conductivity)
```

## Compare instrument types (color points) to YSI data (black points)
###EWLD1 and KALD1 could use calibration

```{r inst_vs_ysi, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=8, fig.fullwidth=TRUE}
allTS0<-StarOddi%>%
  select(Station, DT, Temperature=Temp_C, Salinity=Sal, Conductivity=Cond_mspercm, Instrument)%>%
  bind_rows(RBR)
allTS<-TCM_Temp%>%
  select(Station, DT=`ISO 8601 Time`, Temperature=`Temperature (C)`, Instrument)%>%
  bind_rows(allTS0)

ggplot(allTS, aes(DT,Temperature))+
  geom_point(size=1.1, alpha=0.5, aes(color=Instrument))+
  geom_line(y=-1.8)+
  geom_line(y=-1.5)+
  geom_point(data=YSI)+
  facet_wrap(~Station)+
  theme(legend.position="bottom")+
  theme_cowplot()

ggplot(allTS, aes(DT,Salinity))+
  geom_point(size=1.1, alpha=0.5, aes(color=Instrument))+
  geom_point(data=YSI)+
  facet_wrap(~Station)+
  theme(legend.position="bottom")+
  theme_cowplot()

```

## Difference in readings between instruments

```{r inst_compare, echo=FALSE, message=FALSE, warning=FALSE}

Inst.compare<-StarOddi%>%select(Station, DT, Temp_SO=Temp_C, Sal_SO=Sal)%>%
  full_join(RBR, by=c("Station", "DT"))%>%
  select(Station, DT, Temp_SO, Sal_SO, Temp_RBR=Temperature, Sal_RBR=Salinity)%>%
  full_join(TCM_Temp, by=c("Station", "DT"="ISO 8601 Time"))%>%
  select(Station, DT, Temp_SO, Sal_SO, Temp_RBR, Sal_RBR, Temp_TCM=`Temperature (C)`)

```

```{r compTandS, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
Itable<-Inst.compare%>%
  mutate(Tempdiff_SOvRBR=Temp_SO-Temp_RBR, Tempdiff_TCMvRBR=Temp_TCM-Temp_RBR, Saldiff=Sal_SO-Sal_RBR)%>%
  group_by(Station)%>%
  summarize(mSOvRBR_Temp=mean(Tempdiff_SOvRBR, na.rm=T),
            mTCMvRBR_Temp=mean(Tempdiff_TCMvRBR, na.rm=T),
            mSOvRBR_Sal=mean(Saldiff, na.rm=T))

datatable(Itable, caption="Diffs b/n instruments: TEMP and SAL") %>% 
  formatRound(columns=c("mSOvRBR_Temp","mTCMvRBR_Temp","mSOvRBR_Sal"), digits=3)
```

```{r 1to1, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=11, fig.height=8, fig.fullwidth=TRUE}
Inst.compare%>%filter(Station %in% c("EELD1","EWLD2","JALD2","KALD2"))%>%
  ggplot(aes(Temp_SO, Temp_RBR,color=DT))+
  geom_point(alpha=0.4)+
  scale_color_gradientn(colors = viridis(100), trans="time")+
  geom_abline(intercept=0, slope=1)+
  facet_wrap(~Station)+
  ggtitle("Star Oddi vs RBR Temps")+
  theme_cowplot()

Inst.compare%>%filter(Station %in% c("EELD1","EWLD2","JALD2","KALD2"))%>%
  ggplot(aes(Sal_SO, Sal_RBR,color=DT))+
  geom_point(alpha=0.4)+
  scale_color_gradientn(colors = viridis(100), trans="time")+
  geom_abline(intercept=0, slope=1)+
  facet_wrap(~Station)+
  ggtitle("Star Oddi vs RBR Salinity")+
  theme_cowplot()



```

```{r comptoYSI, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=11, fig.height=8, fig.fullwidth=TRUE}
Ttable<-Inst.compare%>%inner_join(YSI, by=c("DT","Station"))%>%
  select(Station, DT, Temp_YSI=Temperature, Temp_SO, Temp_RBR,Temp_TCM)%>%
  filter(!is.na(DT))
Stable<-Inst.compare%>%inner_join(YSI, by=c("DT","Station"))%>%
  select(Station, DT, Sal_YSI=Salinity, Sal_SO, Sal_RBR)%>%
  filter(!is.na(DT))

datatable(Ttable, caption="Diff in YSI and instruments: TEMPERATURE")%>% 
  formatRound(columns=c("Temp_RBR","Temp_TCM"), digits=3)
datatable(Stable, caption="Diff in YSI and instruments: SALINITY")%>% 
  formatRound(columns=c("Sal_RBR"), digits=3) 
```

##calibrate EWLD1 and KALD1 using YSI data

```{r cal_EWLD_KALD1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=8, fig.fullwidth=TRUE}
source('scr/TScalibration_functions.R')
source('scr/CondtoSal_miliS.R')
EWLD10<-StarOddi%>%filter(Station=="EWLD1")%>%
  left_join(YSI, by=c("Station","DT"))%>%
  mutate(row=1:which(DT==max(DT)))%>%
  rename(fixedCond=Conductivity, fixedTemp=Temperature)
dates<-which(!is.na(EWLD10$fixedCond))#identify where YSI measurements took place, ignore the June ones bc we were off Station
EWLD10$fixedCond[1]<-EWLD10$Cond_mspercm[1]#YSI reading in Aug 2018 doesn't make sense
EWLD10<-EWLD10[c(min(dates):max(dates)),]
EWLD1<-TSmidcal_SO(EWLD10,dates[2])
EWLD1$Salinity<-Cond.to.Sal(EWLD1$fixedCond,EWLD1$fixedTemp)

EWLD1$Station<-"EWLD1_calibratedTC"

EWLD1c<-EWLD1%>%mutate(Salinity=Cond.to.Sal(EWLD1$fixedCond,EWLD1$Temp_C))%>%
  select(-fixedTemp)%>%rename(fixedTemp=Temp_C)
EWLD1c$Station<-"EWLD1_calibratedCond"

KALD10<-StarOddi%>%filter(Station=="KALD1")%>%
  left_join(YSI, by=c("Station","DT"))%>%
  mutate(row=1:which(DT==max(DT)))%>%
  rename(fixedCond=Conductivity, fixedTemp=Temperature)
dates<-which(!is.na(KALD10$fixedCond))#identify where YSI measurements took place, ignore the June ones bc we were off Station
KALD10$fixedCond[1]<-KALD10$Cond_mspercm[1]#no YSI reading in Aug 2018
KALD10$fixedTemp[1]<-KALD10$Temp_C[1]
KALD10<-KALD10[c(1:max(dates)),]
KALD1<-TSmidcal_SO(KALD10,dates[1])
KALD1$Salinity<-Cond.to.Sal(KALD1$fixedCond,KALD1$fixedTemp)

KALD1$Station<-"KALD1_calibratedTC"

KALD1c<-KALD1%>%mutate(Salinity=Cond.to.Sal(KALD1$fixedCond,KALD1$Temp_C))%>%
  select(-fixedTemp)%>%rename(fixedTemp=Temp_C)
KALD1c$Station<-"KALD1_calibratedCond"

calibrated<-bind_rows(EWLD1,EWLD1c, KALD1, KALD1c)%>%
  select(-Temp_C,-Sal,-Cond_mspercm)%>%
  rename(Sal=Salinity,Temp_C=fixedTemp,Cond_mspercm=fixedCond)

StarOddi<-bind_rows(StarOddi,calibrated)

```

##T vs S to check for erroneous data
```{r TvsS, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=8, fig.fullwidth=TRUE}

xsc<-c(0,10,20,45)
xtc<-c(0,-.55,-1.091,-2.515)
mod<-lm(xtc~xsc)


ggplot(StarOddi, aes(Sal, Temp_C,color=DT))+
  geom_point()+
  geom_abline(slope = mod$coefficients[2], intercept = mod$coefficients[1])+
  scale_color_gradientn(colors = viridis(100), trans="time")+
  facet_wrap(~Station)+
  ggtitle("StarOddi")+
  theme_cowplot()

ggplot(RBR, aes(Salinity, Temperature,color=DT))+
  geom_point()+
  geom_abline(slope = mod$coefficients[2], intercept = mod$coefficients[1])+
  scale_color_gradientn(colors = viridis(100), trans="time")+
  facet_wrap(~Station)+
  ggtitle("RBR")+
  theme_cowplot()
```


###What to remove ("anom" data is below TS line givin instrument precision)

```{r Id_anom, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=8, fig.fullwidth=TRUE}
source('scr/TSoutliers_functions.R')

RBR2<-TSanom_workup(RBR, "Temperature", "Conductivity", .002,.01)
SO2<-TSanom_workup(StarOddi, "Temp_C", "Cond_mspercm", .1,2)

ggplot(RBR2, aes(DT,Salinity))+
  geom_point(size=1.1, alpha=0.5, aes(color=anom))+
  facet_wrap(~Station)+
  theme(legend.position="bottom")+
  theme_cowplot()

ggplot(SO2, aes(DT,Sal))+
  geom_point(size=1.1, alpha=0.5, aes(color=anom))+
  facet_wrap(~Station)+
  theme(legend.position="bottom")+
  theme_cowplot()
```
#Choose datasets to use in final table
##color=StarOddi, black=RBR
##use KALD1 calibrated for Temp and Cond, EWLD1 calibrated for Cond
```{r chose_datasets, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=8, fig.fullwidth=TRUE}


SO2%>%filter(Station %in% c("KALD1","KALD1_calibrated","KALD1_calibratedCond","KALD2"))%>%
  ggplot(aes(DT,Sal))+
  geom_point(size=1.1, alpha=0.5, aes(color=Station))+
  geom_point(data=RBR2[RBR2$Station=="KALD2",],aes(DT,Salinity), alpha=0.6)+
  theme_cowplot()+
  theme(legend.position="bottom")

SO2%>%filter(Station %in% c("KALD1","KALD1_calibrated","KALD1_calibratedCond","KALD2"))%>%
  ggplot(aes(DT,Temp_C))+
  geom_point(size=1.1, alpha=0.5, aes(color=Station))+
  geom_point(data=RBR2[RBR2$Station=="KALD2",],aes(DT,Temperature), alpha=0.6)+
  theme_cowplot()+
  theme(legend.position="bottom")

SO2%>%filter(Station %in% c("EWLD1","EWLD1_calibrated","EWLD1_calibratedCond","EWLD2"))%>%
  ggplot(aes(DT,Sal))+
  geom_point(size=1.1, alpha=0.5, aes(color=Station))+
  geom_point(data=RBR2[RBR2$Station=="EWLD2",],aes(DT,Salinity), alpha=0.6)+
  theme_cowplot()+
  theme(legend.position="bottom")

SO2%>%filter(Station %in% c("EWLD1","EWLD1_calibrated","EWLD1_calibratedCond","EWLD2"))%>%
  ggplot(aes(DT,Temp_C))+
  geom_point(size=1.1, alpha=0.5, aes(color=Station))+
  geom_point(data=RBR2[RBR2$Station=="EWLD2",],aes(DT,Temperature), alpha=0.6)+
  theme_cowplot()+
  theme(legend.position="bottom")





##Select the datasets
SO3<-SO2%>%filter(Station !="KALD1"&Station!="KALD1_calibratedCond"&
                    Station!="EWLD1"&Station!="EWLD1_calibratedTC")%>%
  mutate(Station=str_sub(Station,1,5),
         calibrated=case_when(Station=="KALD1"|Station=="EWLD1" ~ TRUE))
```


#Next step = Flagging data
##Values below freezing line (with error) are flagged "INV" for Invalid
##Values that are outliers, or appear to be instrument malfunction (as determined by a trained human) are flagged "QM" for Questionable Measurement


```{r flag_data,  echo=FALSE, warning=FALSE, message=FALSE, fig.width=11, fig.height=8, fig.fullwidth=TRUE}
source('scr/data_flag.R')

RBR_final<-RBR_flagged%>%mutate(flags=case_when(flag==T~"QM", anom==T~"INV"))
SO_final<-SO_flagged%>%mutate(flags=case_when(flag==T~"QM", anom==T~"INV"))

ggplot(RBR_final, aes(DT,Salinity))+
     geom_point(size=1.1, alpha=0.5, aes(color=flags))+
     facet_wrap(~Station)+
     theme(legend.position="bottom")

ggplot(SO_final, aes(DT,Sal))+
     geom_point(size=1.1, alpha=0.5, aes(color=flags))+
     facet_wrap(~Station)+
     theme(legend.position="bottom")

ggplot(RBR_final, aes(DT,Temperature))+
     geom_point(size=1.1, alpha=0.5, aes(color=flags))+
     facet_wrap(~Station)+
     theme(legend.position="bottom")

ggplot(SO_final, aes(DT,Temp_C))+
     geom_point(size=1.1, alpha=0.5, aes(color=flags))+
     facet_wrap(~Station)+
     theme(legend.position="bottom")
     
```


# Finalize tables
```{r finalize, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, fig.width=11, fig.height=8, fig.fullwidth=TRUE}
#Finalize and write csvs

#RBR puts NA at date at daylight savings time, grrr
RBR_final<-RBR_final[!is.na(RBR_final$Station),]
RBR_final$DT[is.na(RBR_final$DT)]<-as.POSIXct("2019-03-10 02:00:00")

# remove unneeded cols
RBR_final<-RBR_final%>%select(-anom, -flag)

SO_final<-SO_final%>%select(Station, DT, Temperature=Temp_C, Salinity=Sal, Conductivity=Cond_mspercm,
                             Speed.of.sound=SoundVel_mpers, Instrument,flags,calibrated)


ggplot(RBR_final, aes(DT, Temperature))+
  geom_point(aes(color=Station), alpha=0.5)+
  geom_point(data=SO_final, aes(DT, Temperature, color=Station), alpha=0.5)

ggplot(RBR_final, aes(DT,Salinity))+
  geom_point(aes(color=Station), alpha=0.5)+
  geom_point(data=SO_final, aes(DT,Salinity, color=Station), alpha=0.5)

ggplot(RBR_final, aes(DT, Conductivity))+
  geom_point(aes(color=Station), alpha=0.5)+
  geom_point(data=SO_final, aes(DT,Conductivity, color=Station), alpha=0.5)

ggplot(RBR_final, aes(DT, Sea.pressure))+
  geom_point(aes(color=Station), alpha=0.5)

```

```{r derived-data}
write.csv(RBR_final, "results/BLE LTER RBRCTD 2018to2019.csv")
write.csv(SO_final, "results/BLE LTER StarOddiCST 2018to2019.csv")
```

